Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Create running title.
Draft abstract.

\maketitle

\begin{abstract}

>>>>

\titlerunning{Analysis of magnetic field waveforms}
\maketitle

\begin{abstract}
Magnetic cooling is an alternative to vapor compression with no use of hazarduous gases. The refrigerant is a solid material which reacts to oscillations in magnetic field with changes in temperature. In active magnetic regenerators, this magnetocaloric material and its effect are coupled with an oscillating fluid flow to yield a thermodynamic cooling cycle between cold and hot source temperatures. The literature is abundant with studies on the influence of the fluid flow waveform on magnetic refrigeration devices, but the influence of the magnetic field waveform is less investigated. In this work, we simulate a previously developed active magnetic regenerator numerical model with different mathematically-defined waveforms, and determine which operating parameters yield the highest values for cooling capacity and coefficient of performance. Results show that the highests performance levels are achieved when the magnetic field is kept constant for the same duration of the fluid flow through the magnetized material, and that the transition times between high and low levels of the magnetic field should be as fast as possible.
